\bibliographystyle{plain}
\begin{thebibliography}{4}
	%chapter 1
	\bibitem{quidinh} Quy định việc cung cấp, sử dụng Internet của chính phử. Truy xuất từ: https://thuvienphapluat.vn/van-ban/Cong-nghe-thong-tin/Nghi-dinh-72-2013-ND-CP-quan-ly-cung-cap-su-dung-dich-vu-Internet-va-thong-tin-tren-mang-201110.aspx. 
	\bibitem{karlova1} Karlova, Natascha, Fisher Karen. A Social Diffusion Model of Misinformation and Disinformation for Understanding Human Information Behaviour. Information Research, 2013, pp. 1-17.
	\bibitem{APhack}Tin tặc giả mạo đăng tin sai lêch trên hãng thông tấn Associated Press. Truy xuấttừ:https://www.usatoday.com/story/theoval/2013/04/23/obama-carney-associated-press-hack-white-house/2106757
	\bibitem{Anhhuong} Ảnh hưởng của MXH với bầu cử Pháp. Truy xuất từ:  https://baomoi.com/facebook-va-phep-thu-mang-ten-bau-cu-phap/c/22045463.epi.
	\bibitem{ebola} Tin đồn dịch Ebola bùng phát tại Hà Nôi. Truy xuất từ: http://baophapluat.vn/tin-nong/lam-ro-danh-tinh-2-nguoi-tung-tin-don-that-thiet-ve-benh-dich-ebola-194152.html
	\bibitem{formusa} Tin đồn công ty Formusa xả thải chưa qua xử lí. Truy xuất từ: http://m.vietnamnet.vn/vn/thoi-su/moi-truong/bo-tn-mt-bac-bo-tin-don-formosa-phat-thai-dioxin-370436.html
	\bibitem{dieuduong} Phóng sự về nghề điều dưỡng viên xuất khẩu lao động tại Đức. Truy xuất từ: https://baomoi.com/du-hoc-sinh-duc-phan-doi-phong-su-cua-vtv-ve-nghe-dieu-duong-vien-luong-thang-100-trieu/c/21365466.epi
	
	%chapter 2
	\bibitem{zhang1} H Zhang, M. Alim, M. T. Thai, and H. Nguyen, Monitor Placement to Timely Detect Misinformation in Online Social Networks, in Proceedings of the 2015 IEEE International Conference on Communications (ICC), 2015.
	\bibitem{kemple1} D. Kempe, J. Kleinberg, and E. Tardos. 2003. Maximizing the spread of influence through a social network. In Proceedings of the ninth ACM SIGKDD international conference on Knowledge discovery and data mining. Washington, DC, USA, 137-146. https://doi.org/10.1145/956750.956769. 
	\bibitem{kemple2} D. Kempe, J. Kleinberg, and E. Tardos. Influential Nodes in a Diffusion Model for Social Networks. In ICALP, 2005, pp. 1127-1138.
	\bibitem{Golden} J. Goldenberg, B. Libai, and E. Muller. Talk of the Network: A Complex Systems Look at the Underlying Process of Word-of-Mouth. Marketing Letters, 2001, pp. 211-223
	\bibitem{Carnes} T. Carnes, R. Nagarajan, S. M. Wild, and A. V. Zuylen. Maximizing Influence in a Competitive Social Network: a Follower’s Perspective. In Proceedings of the Ninth International Conference on Electronic Commerce, 2007, pp. 351-360.
	\bibitem{leskovec} J. Leskovec, M. Mcglohon, C. Faloutsos, N. Glance, and M. Hurst. Cascading Behavior in Large Blog Graphs. In Proceedings of the 2007 SIAM International Conference on Data Mining, 2007, pp. 551-556.
	\bibitem{pedro} Pedro Domingos and Matthew Richardson. Mining the Network Value of Customers. In Proceedings of the Seventh ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, 2001, pp. 57-66.
	
	\bibitem{goyal} A. Goyal, W. Lu, L. V.S. Lakshmanan. Celf++: Optimizing the Greedy Algorithm for Onfluence Maximization in Social Networks. In Proc. WWW, 2011, pp. 47-48.
	\bibitem{snam} A. Goyal, F. Bonchi, L. V. S. Lakshmanan, and S. Venkatasubramanian.: On minimizing budget and time in influence propagation over social networks. Social Network Analysis and Mining, 2(1), 179--192 (2012)
	\bibitem {chen} Wei Chen, Laks V.S. Lakshmanan, and Carlos Castillo. Information and Influence Propagation in Social Networks. A Publication in the Morgan \& Claypool Publishers series Synthesis Lectures on Data Management, 2014.
	\bibitem{qazvin} V. Qazvinian, E. Rosengren, D. R. Radev, and Qiaozhu Mei. Rumor has it: Identifying Misinformation in Microblogs. In Proc. EMNLP, 2011, pp. 1589-1599.
	\bibitem{kwon} S. Kwon, M. Cha, K. Jung, W. Chen, and Y. Wang. 2013. Prominent Features of Rumor Propagation in Online Social Media. In Proc. ICDM, 2013, pp. 1103-1108.
	\bibitem{nguyen1} D. T. Nguyen, N. P. Nguyen, and M. T. Thai. Sources of Misinformation in Online Social Networks: Who to Suspect. In Proceedings of the IEEE Military Communications Conference, 2012.
	\bibitem{nguyen9} Nam P. Nguyen, Guanhua Yan, My T. Thai (2013), "Analysis of misinformation containment in online social networks", Computer Networks.
	\bibitem{nguyen30} D. T. Nguyen, N. P. Nguyen, and M. T. Thai. Sources of Misinformation in Online Social Networks: Who to Suspect. In Proceedings of the IEEE Military Communications Conference, 2012.
	\bibitem{ceren} Ceren Budak, Divyakant Agrawal, Amr El Abbadi, Limiting the Spread of Misinformation in Social Networks.
	\bibitem{zhang31} Huiling Zhang, Md Abdul Alim, Xiang Li, My T. Thai, and Hien T. Nguyen. 2016. Misinformation in online social networks: Detect them all with a limited budget. ACM Trans. Inf. Syst. 34, 3, Article 18 (April 2016), 24 pages. DOI:http://dx.doi.org/10.1145/2885494.
	
	%chapter 3
	\bibitem{zhang32} Zhang Y, Prakash B (2015) Data-aware vaccine allocation over large networks. ACM Trans Knowl Discov Data. https://doi.org/10.1145/2803176.
	\bibitem{zhang33} Zhang H, Alim M, Li X, My TT, Nguyen H (2016a) Misinformation in online social networks: catch them all with limited budget. ACM Trans Inf Syst 34(3):18.
	\bibitem{zhang34} Zhang Y, Adigay A, Saha S, Vullikanti A, Prakash A (2016b) Near-optimal algorithms for controlling propagation at group scale on networks. IEEE Trans Knowl Data Eng. https://doi.org/10.1109/TKDE. 2016.2605088
	\bibitem{twitter} Yadron D (2017) Twitter deletes 125,000 Isis accounts and expands anti-terror teams. The Guardian Web. https://www.theguardian.com/technology/2016/feb/05/ twitter-deletes-isis-accounts-terrorismonline. Accessed 24 June 2017.
	\bibitem{french}  Kottasov I (2017) Facebook targets 30,000 fake accounts in France. CNN media Web. http://money.cnn. com/2017/04/14/media/facebook-fake-news-france-election/index.html. Accessed 24 June 2017.
	\bibitem{zaixin} Zaixin Lu, Wei Zhang, Weili Wu, Joonmo Kim, and Bin Fu. 2011. The complexity of influence maximization problem in the deterministic linear threshold model. Journal of Combinatorial Optimization 24, 3 (April 2011), 374–378. https://doi.org/10.1007/s10878-011-9393-3. 
	\bibitem{vijay38} Vijay V. Vazirani. 2001. Approximation Algorithms. Springer, Verlag New York, Inc. New York, NY, USA.
	\bibitem{vali} L. G. Valiant.: The complexity of enumeration and reliability problems. SIAM Journal on Computing 8(3), 410--421 (1979)
	
	%For TMB
	\bibitem{NetS} DT Nguyen, H Zhang, S Das, MT Thai, TN Dinh.: Least cost influence in multiplex social networks: Model representation and analysis. In: Proceedings of  IEEE 13th International Conference on Data mining, pp. 567--576, IEEE(2013)
	
	\bibitem{AS} J. Leskovec, J. Kleinberg and C. Faloutsos. Graphs over Time.: Densification Laws, Shrinking Diameters and Possible Explanations. In: Proceedings of the 11th ACM SIGKDD international conference on Knowledge discovery in data mining, pp. 177-187, ACM (2005) 
	
	\bibitem{chen10LT} W. Chen, C. Wang, and Y. Wang.: Scalable Influence Maximization in Social Networks under the Linear Threshold Model. In: Proceedings of the 2010 IEEE International Conference on Data Mining, pp. 88-97, IEEE(2010) 
	
	\bibitem{khali} Elias Boutros Khalil, Bistra Dilkina, Le Song.: Scalable Diffusion--Aware Optimization of Network Topology. In: Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining, pp. 1226--1235, ACM (2014)
	
	\bibitem{Jleskovec} J. Leskovec, A. Krause, C. Guestrin, C. Faloutsos, J. M. Van–Briesen, and N. S. Glance.: Cost–effective outbreak detection in networks. In: Proceedings of the 13th ACM SIGKDD international conference on Knowledge discovery and data mining, 420-429, ACM (2007).
	
	% FLE
	\bibitem{amit21} Amit Goyal, Wei Lu, and Laks V.S. Lakshmaman. 2011. SIMPATH: An Efficient Algorithm for Influence Maximization under the Linear Threshold Model. In Proceeding IEEE 11th International Conference on Data Mining. Vancouver, Canada, 211-220. https://doi.org/10.1109/ICDM2011.132.
	
	\bibitem{cha23} M. Cha, A. Mislove, and K.P. Gummadd. 2009. A measurement-driven analysis of infomation propagation in the Flickr social network. In Proceeding of the 18th international conference on World Wide Web (2009). ACM, Madrid, Spain, 721âĂŞ730. htpps://doi.org/10.1145/1526709.1526806.
	
	\bibitem{lesk16} J. Leskovec, L. A. Adamic, and B. A. Huberman. 2007. The dynamics of viral marketing. ACM Transaction on the Web 1, 1 (May 2007). https://doi.org/10.1145/1232722.1232727. 
	
	
	
\end{thebibliography}